Hypertension and microbiome

### 2019-06-05 articletwo.Rmd
fit_asine starts to be ok

@@

    res <- lapply(c2l(var.BP), function(BP)
        fit_asine(pseq.genus.core.comp, variables = c(BP, var.CL)))

    res.trim <- lapply(c2l(var.BP), function(BP)
        lapply(c2l(names(res[[BP]])), function(name) res[[BP]][[name]] %>%
                                                     tidy %>%
                                                     dplyr::filter(grepl(BP, term)) %>%
                                                     mutate(taxa = name)))

>>>>

xor(c(TRUE, TRUE, FALSE), TRUE)

@@

    pseq.genus.core.viruses <- taxa(pseq.genus.core.comp) %>% mygrep(word = "virus$", complement = TRUE)
    pseq.genus.core.comp.pruned <- prune_taxa(pseq.genus.core.viruses, pseq.genus.core.comp)

    res <- lapply(c2l(var.BP), function(BP)
        fit_asine(pseq.genus.core.comp.pruned, variables = c(BP, var.CL)))

    res.trim <- map_df(res, ~map_df(.x, ~tidy(.x), .id = "taxa"), .id = "model")

    adonis <- res.trim %>%
        filter(term %in% var.BP) %>%
        group_by(model) %>%
        dplyr::mutate(q.value = p.adjust(p.value, method="BH")) %>%
        ungroup %>%
        arrange(q.value)

    res$MAP %>% names

adonis %>% pull(taxa) %>% sort

    adonis %>% dplyr::filter(taxa == "g_Sutterella")

map_df(res.trim$HYPERTENSION, ~
